Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-14 journal paper/content/sec-intro.tex
small fixes

We identify the inverted-U relationship driven by the rationality/competitiveness distinctions outlined above: from \HardMax to \HardMaxRandom to \SoftMaxRandom to \Uniform. We also find another, technically different inverted-U relationship which zeroes in on the \HardMaxRandom model. We vary rationality/competitiveness inside this model, and track the marginal utility of switching to a better algorithm.

@@

\xhdr{Significance.}
Our theory takes a basic Bayesian approach, a standard perspective in economic theory, and discovers several strong asymptotic results. The numerical simulations provide a more nuanced and ``non-asymptotic" perspective. In essence, we look for substantial effects within relevant time scales. (In fact, we start our investigation by determining what time scales are relevant in the context of our model.)

>>>>

We identify the inverted-U relationship driven by the rationality/competitiveness distinctions outlined above: from \HardMax to \HardMaxRandom to \SoftMaxRandom to \Uniform. We also find another, technically different, inverted-U relationship which zeroes in on the \HardMaxRandom model. We vary rationality/competitiveness inside this model, and track the marginal utility of switching to a better algorithm.

@@

\xhdr{Significance.}
Our theory takes a basic Bayesian approach, a standard perspective in economic theory, and discovers several strong asymptotic results. The numerical simulations provide a more nuanced and ``non-asymptotic" perspective. In essence, we look for substantial effects within relevant time scales. In fact, we start our investigation by determining what time scales are relevant in the context of our model.
